Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-08-21 paper/re-pro-badge.tex
automatically reproduce paper

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/c2d5cd1}{c2d5cd1} on 2024-08-21 at 09:23:43 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/d86c14f}{d86c14f} on 2024-08-21 at 12:47:34 UTC.
